---
title: "Appendix"
author: "JL"
date: "4/27/17"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
require(xlsx)

# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

Delete this sentence and enter your text here.
```{r}
data <- read.xlsx("dataset.xlsx",1)
```

#Task
You are asked to:
1 - Predict the probability that individual females have diabetes
2 - Detect subsets of characteristics that are at higher risk of diabetes

Deliverables: Wednesday 5/10/17 at noon
1 - Prepare a short report on this study for consumption by the Centers for Diasease Control and Prevention.  The report should contain no more than 3 pages of text. Due Wednesday 5/10/17 at noon. The report should contain a technical appendix.
2 - Email your R markdown file to Professor Matheson so that I can reproduce the technical appendix.

