---
title: "Appendix"
author: "JL"
date: "4/27/17"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
require(xlsx)
require(dplyr)
require(tidyr)
require(randomForest)

# Some customization.  You can alter or delete as desired (if you know what you are doing).
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

Delete this sentence and enter your text here.
```{r}
data <- read.csv("pimaData.csv")
data <- filter(data, Plasma>0, BP>0, BMI>0)
data <- data[-c(1)]
```

```{r}
modInsulin <- lm(Diabetic ~ .,data=data)
modNoInsulin <- lm(Diabetic ~ . - Insulin, data=data)

summary(modInsulin)
summary(modNoInsulin)
```

```{r}
rf <- randomForest(Diabetic~., data=data)
varImpPlot(rf)
```

#Task
You are asked to:
1 - Predict the probability that individual females have diabetes
2 - Detect subsets of characteristics that are at higher risk of diabetes

Deliverables: Wednesday 5/10/17 at noon
1 - Prepare a short report on this study for consumption by the Centers for Diasease Control and Prevention.  The report should contain no more than 3 pages of text. Due Wednesday 5/10/17 at noon. The report should contain a technical appendix.
2 - Email your R markdown file to Professor Matheson so that I can reproduce the technical appendix.

```{r}
summary(data)
hist(data$PRG)
hist(data$Plasma)
hist(data$BP)
hist(data$Thick)
hist(data$Insulin)
hist(data$Body)
hist(data$Pedigree)
hist(data$Age)
hist(data$Response)
```

